Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-05-29 docs/manuscript/manuscript.tex

\begin{abstract}
While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography. 
Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility, the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have kept geographers from conducting more reproduction studies.
This study addresses each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
Our results identify a clear division in perception of reproducibility among geographic sub-fields. 
We also find varying levels of familiarity with reproducible research practices and a perceived lack of incentives to attempt and publish reproduction studies. 
In contrast, many researchers did report attempting to reproduce their own work but not publishing those efforts, which suggests a foundation exists for the examination and expansion of reproducibility in the field.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Reproducible research publicly discloses the evidence used to support claims made in prior work, facilitates the independent verification of those claims, and the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009}.
While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
Nonetheless, reviews of published research papers reveal a lack of data and code for reproducibility \citep{moraila2014measuring, iqbal2016reproducible} and attempts to reproduce published research papers frequently fail \citep[see][]{raghupathi2022reproducibility, chang2015economics}.
Previous studies consistently link the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details or to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
Surveys of researchers find that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
At the same time, a sizable portion of researchers admit engaging in questionable research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.

Many of these same factors may be impacting the reproducibility of geographic research, but they have yet to be systematically measured.
The small number of reproduction studies available within the discipline suggest that most studies are missing the components needed to attempt a reproduction; and of the studies with the needed components, many cannot be fully reproduced \citep[see][]{Kedron2022dimaggio, konkol2019, Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021, paez2022reproducibility}.
The available surveys of research practices in the discipline also support this conclusion as few researchers report sharing their data, metadata, or source code \citep{balz2020reproducibility, konkol2019, ostermann2017}.
At the same time, recent reproduction attempts by \citet{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.

Despite these suggestive findings, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
This knowledge gap exists because researchers conducting reproducibility assessments have not defined clear target populations or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}. 
For example, reproductions of geographic research have focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2022} or on specific topics such as COVID-19 \citep{Holler2023disability, kedron2021GA, paez2022reproducibility}.

More broadly, attempts to catalog or survey reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}, or have drawn samples of researchers from specific journals, members of professional associations, or conference attendees \citep{baker20161}.
These samples of researcher surveys and research papers have been convenient, but are not guaranteed to be representative of researchers and research activity in a particular field through random sampling. 
Like attempts to reproduce specific studies, reproducibility surveys have also focused on evaluating the computational components of research such as data and code availability over less accessible information like field procedures or qualitative analysis that may only be included in text.
Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use. 
The few available surveys of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017} face these same challenges.

@@

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, familiarity and use of reproducible research practices, and the factors they see as barriers to reproducible research using a probability sampling scheme designed to capture the breadth of geographic research.
In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
We then present the results of our survey, first focusing on researcher perceptions and use of reproducible research practices, and then analyzing researcher experiences attempting to reproduce prior work. 
Finally, we discuss the implications of our survey results and conclude by presenting a current snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here.

@@

Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication. 
Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = "Article"} and removed all other publication types (e.g., editorials, book reviews) from our article database. 
We also removed articles with missing authorship information.

@@

Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
We determined uniqueness by grouping researchers by their author-id, and we selected for the most recent contact information by selecting records associated with the most recent year of publication. 
For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.

Applying these criteria yielded a sampling frame of 29,828 researchers. 
On average, these authors published 2.7 articles in geography journals meeting our criteria between 2017 and 2021. 
Roughly one-third (33.0\%) were most recently a corresponding author for an article published in a general geography journal. 
A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).

@@

We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

%%%%%%%
\subsubsection*{Analyzing Researcher Perspectives on Reproducibility}
\noindent We conducted two statistical analyses of the survey responses.
First, we created descriptive statistical summaries of the participant response to assess how geographic researchers define reproducibility, their familiarity and experience with reproducible research practices, and the barriers to reproducibility they perceive in the discipline.

\textit{Definition:} 
We coded participants' qualitative definitions of ``reproducibility'' following two procedures.
First, we measured the similarity of each provided definition to the definition adopted by the \citet{NASEM2019}. 
The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
To make this comparison, each of the authors independently coded each respondent definition for the presence/absence of each of the four characteristics included in the NASEM definition.
Disagreements in the assignment of codes were resolved through discussion between the three authors.
We created an aggregate measure of definition similarity for the final coded response for each participant by counting the presence of each NASEM definition characteristic, resulting in a measure with the domain [0, 4].

Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study--- (i) to facilitate the assessment of prior work, (ii) assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
We derived this coding from common themes in the authors response and our own reading of the reproducibility literature.
As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.

\textit{Familiarity and Experience:} We measured participant familiarity and experience with five reproducibility enhancing research practices: the adoption of open-source software, research notebooks, data sharing, code sharing, and research plan preregistration. 
We created a measure of familiarity by counting the variety of practices a researcher was 'somewhat' or 'very' familiar with.
We measured experience by counting the variety of practices a researcher reported using 'most of the time' or 'always' when conducting their own research. 
Both measures have domains [0, 5].

\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in the discipline. 
From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes 'frequently' or 'occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].

To examine variation in researcher understanding of reproducibility across disciplinary subfields and methodological traditions, we cross tabulated these summary measures and responses to individual questions for these subgroups. 
We then compared response frequencies cross subgroups.

%%%%%%%
\subsubsection*{Analyzing Researcher Reproduction Attempts}
\noindent Our second analysis examined only the responses of researchers that reported attempting a reproduction in the past two years to understand what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.

\textit{Motivations:} To assess what motivated researchers to attempt reproductions, two of the authors independently assigned participants text-based response to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and/or increase the transparency of their work, iii) replication of a study with new data, and iv) a desire to learn from past work, or use the reproduction in teaching. 
We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
We selected groups i) and iv) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.

\textit{Success and Barriers:} To analyze participant success, we create statistical summaries for a series of questions that asked researcher to identify whether they were able to partially or completely recreate some or all results of the target study. 
We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants ability to access key study artifacts (e.g., data, procedural information, code).

Given the topical and epistemological variation that exists among geographic researchers, we again used cross-tabulation to examine differences in response by disciplinary subfield and methodological approach.
However, the size of our sub-sample for this analysis limited number of cross-tabulations we could pursue.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 13.9 percent and the cooperation rate was 77.6 percent, yielding an overall response rate of 10.8 percent. 
The refusal rate was 3.1 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were academics, and they were balanced across career levels from graduate students to full professors as no one career level made up more that 30 percent of the sample.
Respondents were balanced across the disciplinary subfields--- physical geography (29.8\%), geographic methods and GIScience (28.0\%), nature and society (10.1\%), and human geography (30.7\%); and methodological approaches---quantitative (42.2\%), mixed methods (39.0\%), and qualitative (18.3\%).

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Perspectives on Reproducibility}
Reproducibility is on the minds of geographic researchers.
Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%), with half reporting being very familiar with the term (53.6\%).
More pointedly, the majority of survey respondents reported thinking about the reproducibility of their own research (80.7\%), discussing reproducibility with a colleague (70.6\%), and questioning the reproducibility of published work (57.3\%) in the past two years. 
More than half of the researchers we surveyed (52.8\%) also reported considering reproducibility while peer reviewing a grant proposal or publication during the same time frame. 
However, researchers estimated that only 50.6 percent of the results published in the discipline were reproducible, albeit with a large standard deviation of 24.7 percent that suggests a great deal of uncertainty about the true value. 
Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%). 
Strikingly, only a small majority of respondents believe reproducibility is compatible with epistemologies used in the discipline (58.2\%).

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
A total of 181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
Geographic researchers provided definitions of reproducibility that explicitly included an average of 1.83 of the four characteristics from the definition adopted by the NASEM.
This level of inclusion was consistent across subfields and methodological approaches.
The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
This pattern was consistent across subfields and approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and methods focused researchers.
The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data. 
For example, one respondent defines reproducibility as, "The extent to which the research design can be replicated in different geographical contexts."
We observed this alternative definition of reproducibility in 20.4\% of respondents' definitions.

Researchers' definitions of reproducibility were primarily connected to two epistemic functions.
Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies through comparison of original results to results from an attempted reproduction.
These ranged from rigid bitwise quantitative interpretations, as in the "ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which "other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results".
Responses included definitions with a focus on experimental science, as in "an ability to produce consistent results when an experiment is repeated!"

Nearly all other researchers (40.9\%) tied reproducibility to the need for transparency in research so that others could independently expand upon past studies.
For example a quantitative geographers stated: "The methods should provide sufficient information to be able to reproduce the results. In quantitative science this should, at minimum, provide all the equations and algorithms used for any calculation. In the interest of increasing transparency in science, the practice of sharing the code should be encouraged.
For others, open science did not necessarily need to result in identical results: "As a qualitative researcher doing in-depth case study research, my studies can not be perfectly reproduced. But reproducibility sits in the openness about methods and data collection practices, as well as critical reflection about strengths and weaknesses of my research. When we write about those things in the methods section in our papers and theses, their reproducibility is increased." 
The remainder of responses (6.6\%) emphasized repeatable and/or reliable data observation over all other dimensions of reproducibility.
For example, "As a historical geographer, working with qualitative research methods, I understand reproducibility more in terms of sources than of methods. I see reproducible research as being that which makes clear the origin and location of its data."
A physical geographer similarly emphasized data observations: "Data/observations of some variable can be recovered repeatedly by different observers/methods"

Responses to related Likert questions from the full survey sample (\textit{n}=218) support the results from the subsample of 181 qualitative definitions analyzed above.
Identification of reproducibility with both of these functions was supported by responses to related questions from our entire sample (\textit{n}=218). 
A majority of researchers identified reproducibility as important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
Respondents also saw reproducing studies as important to reducing the presence of persistent errors in the discipline (77.5\%) and to increasing trust in research findings (78.45\%).
In parallel with the need for openness and transparency in science, most respondents agreed with the importance of reproducibility for research efficiency (63.3\%), communication with academics (68.8\%) and practitioners (64.7\%), and training students (75.7\%).

@@

%%%%%%%%%%%
\subsubsection*{Familiarity and Experience with Reproducible Research Practices}
Geographic researchers were familiar with an average of 3.26 different reproducible research practices, but only reported experience using an average of 1.44 of these practices in their own work.
More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\%).
However, while familiar with these practices, a far smaller number of researchers reported using these practices regularly in their own work. 
Less than half of the researchers surveyed reported sharing their data (44.5\%), using open source software (38.1\%), using field or lab notebooks to record their work (40.0\%), or sharing their code (18.8\%) most or all of the time. 
Only a small subset of researchers reported familiarity with the pre-registration of research designs and protocols (27.5\%), or regular use of this practice (2.7\%).

Researcher familiarity and use of reproducible research practices also varied by disciplinary subfield and methodological approach. 
Researchers that identified as physical geographers or methodologists and GIScientists reported being familiar with one to two more reproducible researcher practices than human geographers and those focused on nature and society.
Researcher practices similarly diverged by subfield, but no subset of researchers reported using on average more than two of these practices regularly in their work.  
When grouped by methodological approach, quantitative and mixed-methods researchers on average reported familiarity with and use of two more reproducible research practices when compared to qualitative researchers.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion and Conclusion}

>>>>

\begin{abstract}
While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography. 
Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility or the use of reproducible research practices across the discipline's diverse research traditions; nor have we identified the factors that keep geographers from conducting more reproduction studies.
We address each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
Our results identify a clear division in perception of reproducibility among geographic sub-fields. 
We also find varying levels of familiarity with reproducible research practices and a perceived lack of incentives to attempt and publish reproduction studies. 
Despite many barriers to reproducibility and divisions between subfields, we also find common foundations for examining and expanding reproducibility in the field.
These include interest in publishing transparent and reproducible methods, and in reproducing other researchers' studies for a variety of motivations including learning, checking the validity of a prior study, or extending the prior study.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Reproducible research publicly discloses the evidence used to support claims made in prior work, facilitates the independent verification of those claims, and the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009}.
While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
Nonetheless, systematic reviews \citep{moraila2014measuring, iqbal2016reproducible} of published research papers reveal a lack of data and code for reproducibility  and attempts to reproduce published research papers \citep{raghupathi2022reproducibility, chang2015economics} frequently fail.
Previous studies consistently link the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details or to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
Surveys of researchers find that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
At the same time, a sizable portion of researchers admit engaging in questionable research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.

Despite these concerns, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
This knowledge gap exists because researchers conducting reproducibility assessments, surveys of researcher practices, and reproduction attempts have not defined clear target populations for inference, or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}. 
Attempts to catalog or survey reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}, or have drawn samples of researchers from specific journals, members of professional associations, or conference attendees \citep{baker20161}.
These samples are convenient, but are not guaranteed to be representative of researchers and research activity in a particular field. 
Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use. 
Finally, both reproduction attempts and reproducibility surveys have focused on evaluating the computational components of past studies such as data and code availability rather than all aspects of research design and execution.

Reproducibility surveys and reproduction attempts in the geographic literature face these same challenges. 
The few available reproducibility surveys in the discipline have relied on convenience samples drawn from specialist conferences and have only focused on computationally intensive forms of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017}. 
The small number of published attempts to reproduction geographic research similarly have focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021,} or on specific topics such as COVID-19 \citep{Holler2023disability, Kedron2022dimaggio, Kedron2023Beyond, paez2022reproducibility}. 
More recent reproduction attempts by \citet{Kedron2023Beyond} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.

@@

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, perception of reproducibility in their sub-fields,  familiarity and use of reproducible research practices, and the factors they see as barriers to reproducible research.
To support generalization, we used a probability sampling scheme designed to capture the breadth of geographic research.
In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
We then present the results of our survey, first focusing on researcher perceptions and use of reproducible research practices, and then analyzing researcher experiences attempting to reproduce prior work. 
Finally, we discuss the implications of our survey results and conclude by presenting a snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here.

@@

Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication. 
Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = ``Article''} and removed all other publication types (e.g., editorials, book reviews) from our article database. 
We also removed articles with missing authorship information.

@@

Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
We determined uniqueness by grouping researchers by their author-id, and we determined the most recent contact information by selecting records associated with the most recent year of publication. 
For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.

Applying these criteria yielded a sampling frame of 29,828 researchers. 
On average, these authors published 2.7 articles in geography journals meeting our criteria between 2017 and 2021. 
Roughly one-third (33.0\%) were most recently a corresponding author for an article published in a general geography journal. 
A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions had published in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).

@@

We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

We conducted two statistical analyses of the survey responses.
First, we analyzed researcher perspectives on reproducibility by coding and calculating summary variables and statistics for three themes: how geographic researchers define reproducibility, familiarity and experience with reproducible research practices, and perceived barriers to reproducibility.
Second, we analyzed researchers' experiences with reproducing prior studies, for those who had done so, including their motivations and experience of successes and barriers.

\subsubsection*{Analyzing Researcher Perspectives on Reproducibility}

\noindent For our first set of analyses, we examined the full set of survey responses.

\textit{Defining Reproducibility:} 
We coded participants' qualitative definitions of ``reproducibility'' following two procedures.
First, we measured the similarity of each provided definition to the definition adopted by the \citet{NASEM2019}. 
The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
To make this comparison, each of the authors independently coded each respondent definition for the presence/absence of each of the four characteristics included in the NASEM definition.
Disagreements in the assignment of codes were resolved through discussion between the three authors.
We created an aggregate measure of definition similarity for the final coded response for each participant by counting the presence of each NASEM definition characteristic, resulting in a measure with the domain [0, 4].

Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study: (i) to facilitate the assessment of prior work, (ii) assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
We derived this coding from common themes in the responses and our own reading of the reproducibility literature.
As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.

\textit{Familiarity and Experience:} We measured participant familiarity and experience with five reproducibility enhancing research practices: the adoption of open-source software, research notebooks, data sharing, code sharing, and research plan preregistration. 
We created a measure of familiarity by counting the variety of practices a researcher was `somewhat' or `very' familiar with.
We measured experience by counting the variety of practices a researcher reported using `most of the time' or `always' when conducting their own research. 
Both measures have domains [0, 5].

\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in the discipline. 
From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes `frequently' or `occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].

To examine variation in researcher understanding of reproducibility across disciplinary subfields and methodological traditions, we cross tabulated these summary measures and responses to individual questions for these subgroups. 
We then compared response frequencies across subgroups.

%%%%%%%
\subsubsection*{Analyzing Researcher Reproduction Attempts}
\noindent For our second set of analyses, we examined only the responses of researchers who reported attempting a reproduction in the past two years to understand what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.

\textit{Motivations:} To assess what motivated researchers to attempt reproductions, two of the authors independently assigned participants text-based response to groups with the following motivations: i) verify/check published research, ii) learn from published research for extension or teaching, iii) internally check their own research to verify their work and/or increase the transparency of their work, and iv) replicate a study with new data.
We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
We selected groups i) and ii) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.

\textit{Success and Barriers:} To analyze participant success, we create statistical summaries for a series of questions that asked researcher to identify whether they were able to partially or completely recreate some or all results of the target study. 
We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants' ability to access key study artifacts (e.g., data, procedural information, code).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 13.9 percent and the cooperation rate was 77.6 percent, yielding an overall response rate of 10.8 percent. 
The refusal rate was 3.1 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Another \textit{n}=40 authors started the survey, but did not complete enough of the survey to be included in the analysis.

Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were academics, and they were balanced across career levels from graduate students to full professors with no one career level comprising more that 30 percent of the sample.
Respondents identified with each of the four major disciplinary subfields---physical geography (29.8\%), geographic methods and GIScience (28.0\%), nature and society (10.1\%), and human geography (30.7\%); and three major methodological approaches---quantitative (42.2\%), mixed methods (39.0\%), and qualitative (18.3\%).

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Perspectives on Reproducibility}
Reproducibility is on the minds of geographic researchers.
Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%), with half reporting being very familiar with the term (53.6\%).
More pointedly, the majority of survey respondents reported thinking about the reproducibility of their own research (80.7\%), discussing reproducibility with a colleague (70.6\%), and questioning the reproducibility of published work (57.3\%) in the past two years. 
More than half of the researchers we surveyed (52.8\%) also reported considering reproducibility while peer reviewing a grant proposal or publication during the same time frame. 
However, researchers estimated that only 50.6 percent of the results published in the discipline were reproducible, albeit with a large standard deviation of 24.7 percent that suggests a great deal of uncertainty about the true value. 
Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%). 
Strikingly, only a small majority of respondents believe reproducibility is compatible with epistemologies used in their disciplinary subfields (58.2\%).

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
A total of 181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
Geographic researchers provided definitions of reproducibility that explicitly included an average of 1.83 of the four characteristics from the definition adopted by the NASEM.
The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
The pattern of similarity to the NASEM definition and each of its components was consistent across subfields and methodological approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and methods-focused researchers.
The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data. 
For example, one respondent defines reproducibility as, ``the extent to which the research design can be replicated in different geographical contexts."
We observed this alternative definition of reproducibility in 20.4\% of respondents' definitions.

Researchers' definitions of reproducibility were primarily connected to two epistemic functions.
Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies through comparison of original results to results from an attempted reproduction.
These ranged from rigid bitwise quantitative interpretations, as in the ``ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which ``other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results."
Responses included definitions with a focus on experimental science, as in ``an ability to produce consistent results when an experiment is repeated!"

Nearly all other researchers (40.9\%) tied reproducibility to the need for transparency in research so that others could independently expand upon past studies.
For example a quantitative geographer stated: ``The methods should provide sufficient information to be able to reproduce the results. In quantitative science this should, at minimum, provide all the equations and algorithms used for any calculation. In the interest of increasing transparency in science, the practice of sharing the code should be encouraged."
For others, open science did not necessarily need to result in identical results, reflected in this definition: ``As a qualitative researcher doing in-depth case study research, my studies can not be perfectly reproduced. But reproducibility sits in the openness about methods and data collection practices, as well as critical reflection about strengths and weaknesses of my research. When we write about those things in the methods section in our papers and theses, their reproducibility is increased."

The remainder of responses (6.6\%) emphasized repeatable or reliable data observation over all other dimensions of reproducibility.
For example, ``As a historical geographer, working with qualitative research methods, I understand reproducibility more in terms of sources than of methods. I see reproducible research as being that which makes clear the origin and location of its data."
A physical geographer similarly emphasized data observations: ``Data/observations of some variable can be recovered repeatedly by different observers/methods."

Responses to related Likert questions from the full survey sample (\textit{n}=218) support the results from the subsample of 181 qualitative definitions analyzed above.
A majority of researchers identified reproducibility as important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
Respondents also saw reproducing studies as important to reducing the presence of persistent errors in the discipline (77.5\%) and to increasing trust in research findings (78.5\%).
In parallel with the need for openness and transparency in science, most respondents agreed with the importance of reproducibility for research efficiency (63.3\%), communication with academics (68.8\%) and practitioners (64.7\%), and training students (75.7\%).

@@

The data from our sample of researchers has shown broad recognition of reproducibility and its importance in geography with three caveats---confusion between reproducibility and replicability, different perspectives from researchers using qualitative methods, and caution about judging the trustworthiness or validity published research based on its reproducibility. 
In this context, are individual researchers aware of the research practices needed to enhance reproducibility, and have these practices already been adopted for use in research?

%%%%%%%%%%%
\subsubsection*{Familiarity and Experience with Reproducible Research Practices}
Geographic researchers were familiar with an average of 3.26 different reproducible research practices, but only reported experience using an average of 1.44 of these practices in their own work.
More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\%).
However, a far smaller number of researchers reported using these ``familiar" practices regularly in their own work. 
Less than half of the researchers surveyed reported sharing their data (44.5\%), using open source software (38.1\%), using field or lab notebooks to record their work (40.0\%), or sharing their code (18.8\%) most or all of the time. 
Only a small subset of researchers reported familiarity with the pre-registration of research designs and protocols (27.5\%), or regular use of this practice (2.7\%).

Researcher familiarity and use of reproducible research practices varied by disciplinary subfield and methodological approach. 
Researchers that identified as physical geographers or methodologists and GIScientists reported being familiar with one to two more reproducible researcher practices than human geographers and those focused on nature and society.
Researcher practices similarly diverged by subfield, but no subset of researchers reported using on average more than two of these practices regularly in their work.  
When grouped by methodological approach, quantitative and mixed-methods researchers on average reported familiarity with and use of two more reproducible research practices when compared to qualitative researchers.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion and Limitations}
Our survey results indicate that geographic researchers are aware of reproducibility and reproducible research practices, but have yet to incorporate many of those practices into their own work. 
We found that few researchers attempt to independently reproduce the work of others, or to publish the reproduction attempts they do undertake.
In alignment with the broader reproducibility literature, geographic researchers identify the lack methodological transparency and the unavailability of data and procedural information---particularly code---as key barriers to reproducibility in the discipline. 
Our results also suggest the existence of an incentive problem within the discipline, as pressure to publish original research and a lack of oversight create the opportunity to publish irreproducibile work and limited reward for attempting and publishing reproduction studies.  
These findings empirically confirm prior speculations about the reproducibility of geographic research---on the whole, geographers have yet to make reproducible research practices and reproduction attempts a regular part of disciplinary practice.
